A large-scale analysis of racial disparities in police stops across the

### 2019-07-22 lib/paper_results.Rmd
progress

```{r setup, echo = FALSE}
library(tidyverse)
library(knitr)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
pfs <- read_rds(here::here("results", "prima_facie_stats.rds"))
vod <- read_rds(here::here("results", "veil_of_darkness.rds"))
# disp <- read_rds(here::here("results", "disparity.rds"))
mj <- read_rds(here::here("results", "marijuana_legalization_analysis.rds"))
```

@@

```{r veil_of_darkness-plot}
vod$full$plots$states$TX$`6:00pm`
vod$full$plots$states$TX$`6:15pm`
vod$full$plots$states$TX$`6:30pm`
vod$full$plots$states$TX$`6:45pm`
vod$full$plots$states$TX$`7:00pm`
vod$full$plots$states$TX$`7:15pm`
vod$full$plots$states$TX$`7:30pm`
```

@@

\begin{center}
\subsection{Threshold test results}
\end{center}
```{r disparity-city-thresholds-table}
kable(disp$city$threshold$results$aggregate_thresholds)
```
```{r disparity-state-thresholds-table}
kable(disp$state$threshold$results$aggregate_thresholds)
```
\newpage
```{r disparity-city-thresholds-plot, fig.height = 3, fig.width = 7}
disp$city$threshold$plots$aggregate
```
```{r disparity-state-thresholds-plot, fig.height = 3, fig.width = 7}
disp$state$threshold$plots$aggregate
```
\newpage
```{r disparity-city-ppcs, fig.height = 3, fig.width = 7}
disp$city$threshold$ppc$search_rate
```
```{r disparity-state-thresholds-plot, fig.height = 3, fig.width = 7}
disp$city$threshold$ppc$hit_rate
```
\newpage
```{r disparity-state-ppcs, fig.height = 3, fig.width = 7}
disp$state$threshold$ppc$search_rate
```
```{r disparity-state-thresholds-plot, fig.height = 3, fig.width = 7}
disp$state$threshold$ppc$hit_rate
```
\newpage

@@

```{r save_mj_control_search_rates}
# NOTE: have to save the file to the tmp directory because landscape doesn't
# work with r execution blocks
library(ggplot2)
ggsave(
  "/tmp/mj_control_search_rates.png",
  mj$plots$control_search_rates,
  height = 6,
  width = 11
)
```
\begin{landscape}
\includegraphics{/tmp/mj_control_search_rates.png}
\end{landscape}

>>>>

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(knitr)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
pfs <- read_rds(here::here("results", "prima_facie_stats.rds"))
vod <- read_rds(here::here("results", "veil_of_darkness.rds"))
disp <- read_rds(here::here("results", "disparity.rds"))
mj <- read_rds(here::here("results", "marijuana_legalization_analysis.rds"))
```

@@

```{r veil_of_darkness-plot}
vod$full$plots$states$TX$`6:15pm`
vod$full$plots$states$TX$`6:30pm`
vod$full$plots$states$TX$`6:45pm`
vod$full$plots$states$TX$`7:00pm`
vod$full$plots$states$TX$`7:15pm`
```

@@

\begin{center}
\subsection{Threshold test results}
\end{center}
```{r disparity-city-thresholds-table}
kable(disp$city$threshold$results$aggregate_thresholds)
```
```{r disparity-state-thresholds-table}
kable(disp$state$threshold$results$aggregate_thresholds)
```
\newpage
```{r disparity-city-thresholds-plot, fig.height = 3, fig.width = 7}
disp$city$threshold$plots$aggregate
```
```{r disparity-state-thresholds-plot, fig.height = 3, fig.width = 7}
disp$state$threshold$plots$aggregate
```
\newpage
```{r disparity-city-ppc-search, fig.height = 3, fig.width = 7}
disp$city$threshold$ppc$search_rate
```
```{r disparity-city-ppc-hit, fig.height = 3, fig.width = 7}
disp$city$threshold$ppc$hit_rate
```
\newpage
```{r disparity-state-ppc-search, fig.height = 3, fig.width = 7}
disp$state$threshold$ppc$search_rate
```
```{r disparity-state-ppc-hit, fig.height = 3, fig.width = 7}
disp$state$threshold$ppc$hit_rate
```
\newpage

@@

<!-- # ```{r save_mj_control_search_rates} -->
<!-- # # NOTE: have to save the file to the tmp directory because landscape doesn't -->
<!-- # # work with r execution blocks -->
<!-- # library(ggplot2) -->
<!-- # ggsave( -->
<!-- #   "/tmp/mj_control_search_rates.png", -->
<!-- #   mj$plots$control_search_rates, -->
<!-- #   height = 6, -->
<!-- #   width = 11 -->
<!-- # ) -->
<!-- # ``` -->
<!-- \begin{landscape} -->
<!-- \includegraphics{/tmp/mj_control_search_rates.png} -->
<!-- \end{landscape} -->
